Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-10-03 paper.tex
Change up to subsection1

\keywords{Dielectric property, electronic polarizability, two-dimensional material, scaling relation, first principles simulations, dielectric anisotropy}

@@

\begin{abstract}
  The dielectric constant, which defines the polarization of
  the media, is a key quantity in condensed matter. It determines
  several electronic and optoelectronic properties important for a
  plethora of modern technologies from computer memory to field effect
  transistors and communication circuits. Moreover, the importance of
  the dielectric constant in describing electromagnetic interactions
  through screening plays a critical role in understanding fundamental
  molecular interactions. Here we show that despite its fundamental
  transcendence, the dielectric constant does not define unequivocally
  the dielectric properties of two-dimensional (2D) materials due to
  the locality of their electrostatic screening. Instead, the electric
  polarizability correctly captures the dielectric nature of a 2D
  material which is united to other physical quantities in an
  atomically thin layer. We reveal a long-sought universal formalism
  where electronic, geometrical and dielectric properties are
  intrinsically correlated through the polarizability opening the door
  to probe quantities yet not directly measurable including the real
  covalent thickness of a layer. We unify the concept of dielectric
  properties in any material dimension finding a global dielectric
  anisotropy index defining their controllability through
  dimensionality.
\end{abstract}

The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
plays a crucial role in bridging various fundamental material
properties, such as bandgaps\cite{Moss_1950_relation,Moss_1985_n_Eg}, 
optical absorption\cite{kittel_2005_introduction} and 
conductivities\cite{Dressel_2001_electrodynamics}   
with elemental interactions. 
The central place of $\varepsilon$ in solid-state physics drives the analysis of several phenomena 
where is common to classify a material accordingly to its ability to screen an 
electric field $\boldsymbol{E}$ in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
condensed matter physics, as well as in related fields in chemistry and materials science. 
The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
theoretical and experimental techniques of distinct flavors where the probe of the dielectric properties 
is made through an external electric field. 
%
Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
electronic and dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
%
The confined nature of the electrons in such atomically thin space associated with the 
attenuated and anisotropic character of the dielectric screening of 2D crystals 
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
have generated long-standing debates whether the dielectric constant 
may represent their dielectric features or it can be used only as an 
additional parameter from the bulk-counterparts.

%%
%%
We approach this problem showing that the current definition of
$\varepsilon$ used in layered materials is ill defined as illustrated
in Figure \ref{fig-1}.  From the theoretical point of view, an
isolated 2D material is placed in the \textit{xy}-plane of a
periodically repeating superlattice (SL) with a length $L$ along the
\textit{z}-direction separating the cell images. The static macroscopic
dielectric tensor from the superlattice

@@

respectively\cite{Dressel_2001_electrodynamics}:

@@

    &\varepsilon^{pq} &= \kappa^{pq} +

@@

$\boldsymbol{u}$ is the total dipole moments within the SL, $\rho$ is

@@

$\varepsilon_{0}$ is vacuum permittivity. Here we only study the
electronic contribution to the macroscopic dielectric constant where
the dipole $\boldsymbol{P}$ comes from the displacement of electron
cloud under external electric field, while the ionic contribution
\cite{Laturia_2018} ($\boldsymbol{P}$ comes from the displacement of
nuclei) to the static $\varepsilon$ is not considered.
For the majority of the 2D nanosheets, the
off-diagonal elements of the dielectric tensor ($p \neq q$) tend to be
negligible.  Considering that the 2D material is placed in vacuum
($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can distinguish two
components of $\varepsilon$, namely the in-plane
($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane

@@

dipoles along the \textit{z}-direction in a range of 
$\sim{}$5--6 \AA{} into the vacuum (Figure \ref{fig-1}{\textbf a} and
Supplementary Figure \ref{SI-fig:rho-profile}). 

@@

When $L$ is large
enough, the induced dipoles $\boldsymbol{u}$ from the periodic images
do not interact mutually as the integral in Eq. \ref{eq:def-eps-2}
depends only locally on the atomic charge density at the layer.
However, we can see from Eq. \ref{eq:def-eps-1} that both

@@

$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$ via the volume of
the cell $\Omega$. In the case of bulk materials such physical dependence 
is well described given the periodicity of the 3D crystal throughout the space.  

@@

In the case of 2D materials, however, such repetition is artificial along the direction 
perpendicular to the plane. Despite of the simplicity of this argument,  
any calculation performed using such
definition will intrinsically depend on the magnitude of $L$ as an
additional parameter. This dependence can be clearly demonstrated by
plotting $\varepsilon^{\parallel}_{\mathrm{SL}}$ and

@@

theory (DFT) using hybrid functionals (see {\it Theoretical Methods} for details)
as a function of $L$ for P$\bar{6}$m2 transition metal
dichalcogenides (TMDCs), 2H-MX$_{2}$, where M=Mo, W and X=S, Se, Te
(top panels of Figure \ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c},
respectively). Both components of the dielectric constant 
change systematically with $L$ without a clear convergence. 

@@

Simulations performed at higher levels of theory using many-body
techniques, G$_{\rm 0}$W$_{0}$, invariably give alike results (see
Supplementary Figure \ref{SI-fig:GW-PBE-alpha}).  We have also
undertaken similar analysis into the frequency ($\omega$) regime for
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ where the $L$-dependence
remains present despite various methods utilized (see Supplementary
Section \ref{SI-ssec:gw} for a systematic study).  These results
indicate that quantities that depend on
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, for instance, the optical
absorption, suffer the same deficiencies.
% Moreover, due to the long range Coulomb
% interaction, variations of the quasi-particle energy (and
% corresponding peak positions) with lattice constant $L$ at the
% G$_{0}$W$_{0}$ level is observed (details see Supplementary Section
% SXX). Such results implicate that several other related quantities,
% including the optical absorption and optical conductivity, suffer the
% same deficiencies, which should be avoided in a fully first principles
% theory.
%as the computation of the dielectric function is based on alike formalism\cite{Ehrenreich-Cohen paper}
% We can understand this behavior in terms of the electrostatic of the problem. 
%This result indicates that the use of the dielectric constant to represent 
%dielectric properties at the static limit of a 2D material is 
%ambiguous as the long-range correlations between the layers would only 
%be negligible at the limit of $L \rightarrow \infty$, which incidentally modify the magnitudes of 
%$\varepsilon^{\parallel, \perp}_{\mathrm{SL}}$ in the convergence. 
It is worth mentioning that experimental dielectric results of 2D
materials generally need to define an ``effective thickness'' of the sheet
to interpret ellipsometry data
\cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, reflectance or
transmission spectra \cite{Li_2014, Yoffe-Wilson69} in order to
extract information for the real part of the dielectric functions.  We
argue that such procedure may induce inevitably variations of the
results as the thickness is normally chosen by the interlayer spacing
of the respective bulk materials (see Supplementary Section
\ref{SI-sec:2D-3D-rescale}).
%%%
% We observe that neither
% $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
% $\varepsilon^{\perp}_{\mathrm{SL}}$ converges with $L$ due to fact
% that the long-range Coulomb interaction could not be completed
% screened within the range of magnitudes computationally accessible
%.
%As a result, the $L$-dependency of $\varepsilon_{\mathrm{SL}}$ makes
%it impractical to represent the dielectric nature of a 2D material
%both theoretically and experimentally, because the size of vacuum
%layer must always be considered. 

To solve this problem, we need to find the $L$-independent alternative
of $\varepsilon_{\mathrm{SL}}$, which is related to both electrostatic
and optical properties of a 2D material \cite{Matthes_2016}. As
described before, by multiplying Eq.~\ref{eq:def-eps-2} with $L$ we
obtain the sheet polarization density
$\boldsymbol{\mu}_{\mathrm{2D}}$, that is,
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, which is
independent of $L$ due to the locality of $\boldsymbol{u}$ and $A$.
Similar to the definition of molecular polarizability
\cite{Israelachvili_2011}, $\boldsymbol{\mu}_{\mathrm{2D}}$ is
associated with the 2D polarizability $\alpha_{\mathrm{2D}}$ through:

@@

electric field. Using electrostatic boundary conditions, the
continuity of the electric field along the in-plane direction gives
$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$
\cite{Markel_2016}. For the out-of-plane component, the dipole
screening yields

@@

\cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we can relate the 2D
polarizabilities, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ with

@@

Note due to the choice of $\varepsilon$ is limited to the electronic
macroscopic dielectric constant, $\alpha_{\mathrm{2D}}$ naturally
refers to the electronic polarizability (the polarizability of the
electron cloud \cite{Israelachvili_2011}). We also note that such

@@

@@

The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the

@@

of the selected TMDCs as a function of $L$, calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}. We observe
that both $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ reached 
convergence in a much shorter vacuum length within 10 \AA ~and 15 \AA, respectively. 

@@

Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can also be used to remove 
the dependence of $L$ on $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ via $\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$, respectively (Supplementary Section \ref{SI-ssec:gw}). 

@@

These findings provide that the 2D polarizability captures the essence
of the dielectric properties of layered materials as the microscopic
quantity in describing the atomic interactions present in the
layers. Its local nature removes the dependence on size effects
present in the calculations.  More discussions about the choice of the

>>>>

\keywords{Dielectric screening, electronic polarizability, two-dimensional material, scaling relation, first principles simulations, dielectric anisotropy}

@@

\begin{abstract}
  The dielectric constant, which defines the polarization of
  the media, is a key quantity in condensed matter. It determines
  several electronic and optoelectronic properties important for a
  plethora of modern technologies, and its importance of 
  % from computer memory to field effect
  % transistors and communication circuits. Moreover, the importance of
  % the dielectric constant in
  describing electromagnetic interactions through screening plays a
  critical role in understanding fundamental molecular
  interactions. Here we show that despite its fundamental
  transcendence, the dielectric constant does not define unequivocally
  the dielectric properties of two-dimensional (2D) materials due to
  the locality of their electrostatic screening. Instead, the
  electronic polarizability correctly captures the dielectric nature
  of a 2D material which is united to other physical quantities in an
  atomically thin layer. Being a quantity with unique definition, the
  electronic polarizability overcomes the disadvantage of uncertainty
  posed by the effective dielectric constant model conventionally used
  to described screening in 2D material systems.  Furthermore, we
  reveal a long-sought universal formalism where electronic,
  geometrical and dielectric properties are intrinsically correlated
  through the polarizability opening the door to probe quantities yet
  not directly measurable including the real covalent thickness of a
  layer. Lastly, we unify the concept of dielectric properties in any
  material dimension finding a global dielectric anisotropy index
  defining their controllability through dimensionality.
\end{abstract}

\pagebreak{}

\section{Introduction}
\label{sec:introduction}

The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
plays a crucial role in bridging various fundamental material
properties, such as bandgaps\cite{Moss_1950_relation,Moss_1985_n_Eg}, 
optical absorption\cite{kittel_2005_introduction} and 
conductivities\cite{Dressel_2001_electrodynamics}   
with elemental interactions. 
The central place of $\varepsilon$ in solid-state physics drives the analysis of several phenomena 
where is common to classify a material accordingly to its ability to screen an 
electric field $\boldsymbol{E}$ in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
condensed matter physics, as well as in related fields in chemistry and materials science. 
The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
theoretical \cite{Adler_1962,Hybertsen_1987} and experimental techniques \cite{palik_1998handbook} of distinct flavors
% where the probe of the dielectric properties 
% is made through an external electric field. 
%
Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
% electronic and
dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
%
The confined nature of such atomically-thin 2D crystals associated
with the attenuated and anisotropic character of the dielectric
screening
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
have generated long-standing debates whether the dielectric constant
truly represents dielectric features of such low-dimensional systems,
% or it can be used only as an
% additional parameter from the bulk-counterparts.
The controversy of
$\varepsilon$ values reported by both theoretical and experimental
approaches can be widely seen throughput literature\cite{Li_2016},
where the variation of $\varepsilon$ can be more than one order of
magnitude. As a consequence, several key physical parameters that
scales with $\varepsilon$, such as the exciton binding energy and
Debye screening length, cannot be reliably estimated due to the
discrepancy of reported $\varepsilon$ values. In this letter, we give
a thorough study of the underlying issue. Using \textbf{ab initio}
simulations of a model system, we demonstrate that the macroscopic
dielectric constant strongly depends on the size of the superlattice,
making it unsuitable to describe the screening of a 2D material. On
the contrary, by analyzing the formalism of dielectric tensors, we
propose that the electronic polarizability is the true descriptor
which uniquely captures the dielectric nature of 2D materials. The 2D
electronic polarizability has unique definition, which overcomes the
disadvantage of ambiguity compared with the conventionally used
effective dielectric medium model for 2D materials. Moreover, we show
the universal scaling relations for in- and out-of-plane 2D electronic
polarizabilities with the electronic and geometric information of the
2D material. The concept of electronic polarizabilities bridges the
gap between the dielectric properties of 2D and 3D systems, and can be
extended to characterize the dielectric anisotropy for any material
dimensions.

%%
%%

\section{Results and discussions}
\label{sec:results-discussions}

\subsection{Lattice-dependency of macroscopic dielectric constant}
\label{sec:latt-depend-macr}

We first approach the discrepancy of macroscopic dielectric constant
of 2D materials, by showing that the current definition of
$\varepsilon$ used in layered materials is ill defined.  This can be
viewed in a model system as illustrated
in Figure \ref{fig-1}, where an isolated 2D material is placed in
the \textit{xy}-plane of a periodically repeating superlattice (SL)
with a length $L$ along the \textit{z}-direction separating the cell
images. The static macroscopic dielectric tensor from the superlattice

@@

respectively~\cite{Dressel_2001_electrodynamics}:

@@

    &\varepsilon_{\mathrm{SL}}^{pq} &= \kappa^{pq} +

@@

$\boldsymbol{u}$ is the total dipole moment within the SL, $\rho$ is

@@

$\varepsilon_{0}$ is vacuum permittivity. Here we limit out study on
the electronic contribution to the macroscopic dielectric constant
where the dipole $\boldsymbol{P}$ comes from the displacement of
electrons under external field.  On the other hand, the ionic
contribution to $\varepsilon_{\mathrm{SL}}$ that comes from
displacement of atomic nuclei is not covered in this due to its
complex dependency on several factors including phonon
dispersion~\cite{Sohier_2017} as well as lattice
symmetry~\cite{Laturia_2018}, which requires separated discussions.
The symmetry of 2D materials lead to the negligible off-diagonal
elements of the dielectric tensor ($p \neq q$), while and diagonal
elements $\varepsilon_{\mathrm{SL}}^{xx}$,
$\varepsilon_{\mathrm{SL}}^{yy}$ and $\varepsilon_{\mathrm{SL}}^{zz}$
can be different \cite{Sohier_2016}.  Considering that the 2D material
is placed in vacuum ($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can
distinguish two components of $\varepsilon_{\mathrm{SL}}$, namely the
in-plane ($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane

@@

dipoles along the \textit{z}-direction within a range of $\sim{}$5--6
\AA{} into the vacuum (Figure \ref{fig-1}{\textbf a} and Supplementary
Figure \ref{SI-fig:rho-profile}).

@@

Under a certain external field, when $L$ increases, the confinement of
the induced dipole moment $\boldsymbol{u}$ causes the integral in the
numerator of Eq.~\ref{eq:def-eps-2} to be saturated, when the
separation is large enough such that dipole moment from periodic
images do not mutually interfere. On the other hand, the increase of
$L$ in the denominator of Eq.~\ref{eq:def-eps-2} dilutes the polarization density, and in turn makes both

@@

$\varepsilon^{\perp}_{\mathrm{SL}}$ dropping to
unity when $L$ is infinitely large.
% In the case of bulk materials
% such physical dependence is well described given the periodicity of
% the 3D crystal throughout the space.

@@

% In the case of 2D materials, however, such repetition is artificial along the direction 
% perpendicular to the plane.
Despite of the simplicity of this argument, any calculation performed
using such definition will intrinsically depend on the magnitude of
$L$, an artificial parameter introduced by simulation system. This
dependence can be clearly demonstrated by plotting

@@

theory (DFT) (see {\it Theoretical Methods} for details) as a function
of $L$ for P\={6}m2 transition metal dichalcogenides (TMDCs),
2H-MX$_{2}$, where M=Mo, W and X=S, Se, Te (top panels of Figure
\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c}, respectively). To
get a better description of the electronic band structure, the
calculations of dielectric properties were performed at the level of
Heyd-Scuseria-Ernzerhof (HSE06) hybrid functional
\cite{Heyd_2003,Heyd_2006}.  Both components of the dielectric
constant decreases with $L$ as excepted. To rule out the possibility
that the result is affected by the choice of \textbf{ab initio}
methods, we also performed simulations at higher levels of theory
using many-body techniques (G$_{0}$W$_{0}$), which invariably give
alike results (see Supplementary Figure \ref{SI-fig:GW-PBE-alpha}).
The lattice-size dependency also exists for dielectric function in the
frequency ($\omega$) domain. We carried out similar analysis for
frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, as seen in
Supplementary Section \ref{SI-ssec:gw}. Despite the different levels
of techniques used (Perdew-Burke-Ernzerhof (PBE) exchange-correlation
functional \cite{Perdew_1996,Ernzerhof_1999,Paier_2005}, HSE06 hybrid
functionals or G\textsubscript{0}W\textsubscript{0} method), the
magnitude of dielectric functions calculated universally decreases
with $L$ over the frequency domain.  These results indicate that
quantities that depend on
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, including the optical
absorption and electron energy loss spectrum (EELS), suffers the same
deficiencies as $\varepsilon_{\mathrm{SL}}$ for 2D materials. This
simple model system explains the origin of the discrepancy of dielectric constant values reported in previous literature~\cite{Li_2016}.

{\color{magenta}
It is worth mentioning that experimental dielectric results of 2D
materials generally need to define an ``effective thickness'' of the sheet
to interpret ellipsometry data
\cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, reflectance or
transmission spectra \cite{Li_2014, Yoffe-Wilson69} in order to
extract information for the real part of the dielectric functions.  We
argue that such procedure may induce inevitably variations of the
results as the thickness is normally chosen by the interlayer spacing
of the respective bulk materials (see Supplementary Section
\ref{SI-sec:2D-3D-rescale}).
}
%
%%%
%
% We observe that neither
% $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
% $\varepsilon^{\perp}_{\mathrm{SL}}$ converges with $L$ due to fact
% that the long-range Coulomb interaction could not be completed
% screened within the range of magnitudes computationally accessible
%.
%
%
%As a result, the $L$-dependency of $\varepsilon_{\mathrm{SL}}$ makes
%it impractical to represent the dielectric nature of a 2D material
%both theoretically and experimentally, because the size of vacuum
%layer must always be considered. 
%

\subsection{The electronic polarizability of 2D materials}
\label{sec:electr-polar-2d}

To solve the problem described above, we need to find the
$L$-independent alternative of $\varepsilon_{\mathrm{SL}}$, which is
related to both electrostatic and optical properties of a 2D
material~\cite{Matthes_2016}. By multiplying Eq.~\ref{eq:def-eps-2}
with $L$, we obtain the sheet polarization density that is,
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, in
direction $p$. Following the discussion in the previous section,
$\boldsymbol{\mu}_{\mathrm{2D}}^{p}$ becomes independent of lattice
size when $L$ is large enough, due to the saturation of
$\boldsymbol{u}^{p}$.

@@

Similar to the molecular polarizability \cite{Israelachvili_2011}, we
can define a 2D electronic polarizability $\alpha_{\mathrm{2D}}$ which
characterizes the ability to induce dipole moment of a 2D material. It
is associated with $\boldsymbol{\mu}_{\mathrm{2D}}$ through:

@@

electric field causing the polarization. At $L \rightarrow \infty$
limit, $E_{\mathrm{loc}}$ can be solved using electrostatic boundary
conditions of slab geometry \cite{Markel_2016}. The continuity of the
electric field along the in-plane direction gives
$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$,
while for the out-of-plane component, the dipole screening yields

@@

\cite{Meyer_2001_dipole_slab,T_bik_2004}, where
$\boldsymbol{E}^{\parallel}$ and $\boldsymbol{E}^{\perp}$ are the
external field in the in-plane and out-of-plane directions,
respectively. Combining with Eqs. \ref{eq:def-eps-1} and
\ref{eq:def-eps-2},
can be related with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and

@@

% 20191003-16:00
% As pointed before, as we limit the discussion on electronic contributions to the dielectric properties, $\alpha_{\mathrm{2D}}$ characterizes the polarizability of electron cloud of a 2D materials.
% refers to the electronic polarizability (the polarizability of the
% electron cloud \cite{Israelachvili_2011}).
{\color{magenta} We also note that such

@@

}

@@

Using these relations, we show the calculated

@@

of the selected TMDCs as a function of $L$ in the bottom panels of
Figure \ref{fig-1}b and \ref{fig-1}c, respectively.  In contrast to
$\varepsilon_{\mathrm{SL}}^{\perp}$, We observe that both
reach convergence when $L$ exceeds 10 \AA and 15 \AA, respectively.
{\color{red} Convergence plot in SI} Such result is in good agreement
with the spatially localized induced dipole moment of a 2D materials
as shown in Supplementary Figure~\ref{SI-fig:rho-profile}. 

@@

Such relations can also be used to remove the dependence on $L$ for
frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, generating
lattice-independent electronic polarizability
$\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$ in the frequency domain,
respectively (details see Supplementary Section \ref{SI-ssec:gw}).

@@

These findings indicate that the electronic polarizability $\alpha_{\mathrm{2D}}$ captures the essence
of the dielectric properties of 2D materials. In contrast to the ill-defined macroscopic $\varepsilon_{\mathrm{SL}}$, $\alpha_{\mathrm{2D}}$ has unique definition, and does not suffer from the dependency on the lattice size.
More discussions about the choice of the
